On the Dynamics of Anthropomorphism in Robotics

### 2013-07-01 dynamics-anthropomorphism.tex
Detail what 'introspective' means

If the unexpected behavior is not planned, and perceived as such by the human
(case I), the human can interpret that the robot is able to fail. If the robot
explicitly states its failure (for instance, by saying ``I'm lost!''), the
behavior is then called \emph{transparent} \fixme{cite here, Julia?} \hl{(literature on transparency)}, and the
user may besides hypothesize that the robot has \emph{introspective}
capabilities \hl{(what is this?)}, which in turn may leads to higher anthropomorphism level.  On the
contrary, if the robot shows no sign of recognizing its own failure, the user
may ascribe a lower level of anthropomorphism to the robot.

>>>>

If the unexpected behavior is not planned, and perceived as such by the human
(case I), the human can interpret that the robot is able to fail. If the robot
explicitly states its failure (for instance, by saying ``I'm lost!''), the
behavior is then called \emph{transparent} \fixme{cite here, Julia?} \hl{(literature on transparency)}, and the
user may besides hypothesize that the robot has \emph{introspective}
capabilities (it can reflect on its own internal state), which in turn may
leads to higher anthropomorphism level.  On the contrary, if the robot shows no
sign of recognizing its own failure, the user may ascribe a lower level of
anthropomorphism to the robot.
